MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-14 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
comment out nonessential code for testing

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preAdjustedSigCovars.NULL, fig.width=20, fig.height=12}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

>>>>

<!-- ### Significant Covariates -->
<!-- Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates -->
<!-- ```{r preAdjusted.covariates, cache=TRUE} -->
<!-- # Find correlation between PC's of gene expression with covariates -->
<!-- preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E,  -->
<!--                                                  COVARIATES, -->
<!--                                                  'NULL design(voom-normalized)',  -->
<!--                                                  isKeyPlot=TRUE,  -->
<!--                                                  MIN_PVE_PCT_PC = 1) -->
<!-- ``` -->

<!-- Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars` -->
<!-- ```{r preAdjustedSigCovars.NULL, fig.width=20, fig.height=12} -->
<!-- preAdjustedSigCovars[["PC_res"]][[2]]$plotData -->
<!-- ``` -->
